Appendix for: "Bad Forecast, Good Decision

### 2021-02-05 manuscript/appendix.Rmd
WIP

with $r_3 = 0.002$, $K_3 = 10$ and $\sigma_3 = 0.05$:

@@

fig3a <- 
  d %>% pivot_longer(names(models), "model") %>%
  ggplot(aes(state, value, col=model, lty=model)) +
  geom_hline(aes(yintercept = 0), lwd=1) + 
  geom_line(lwd=2, show.legend = FALSE) + 
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x))) + xlab("x")
```

>>>>

with $r_3 = 0.002$, $K_3 = 10$ and $\sigma_3 = 0.05$.

@@

fig3a <- 
  d %>% pivot_longer(names(models), "model") %>%
  ggplot(aes(state, value, col=model, lty=model)) +
  geom_hline(aes(yintercept = 0), lwd=1) + 
  geom_line(lwd=2, show.legend = FALSE) + 
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x) - x)) + xlab("x")
```
